The Effect of Void on the

### 2018-10-04 draft/alexpub.tex
add ref
add no
delete blank line
delet 1 line

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\bibliography{ref/VIOLET-ref.bib}

@@

	\subsection{Analysis method}
	The centrosymmetry parameter is defined as follow:
	\begin{equation} \label{eq:csp} 
	P = \displaystyle\sum_{i=1}^{6}|\vec{R_i}+{\vec{R}}_{i+6}|^2
	\end{equation}

@@

	\section{Results and Discussion}
%	/home/alex/Documents/violet/draft/img/perfect-line.pdf

	\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/perfect-line2-2}
		\caption{perfect-line2-2}
		\label{fig:perfect-line2-2}
	\end{figure}

@@

\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
The volume defects considered pertain to three-dimensional objects contained within a matrix. Three-dimensional structures composed of zero-, one- or two-dimensional defects are not considered here.
Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, more or less (as possibly associated with
the occurrence of incoherent or coherent interfaces; see Sect. 5.3), the long-range translation symmetry of the matrix. They may induce considerable misfit-stress fields and thus can influence material properties pronouncedly. Such stress fields surrounding the second-phase particles can be due to misfit between the volume occupied by the second-phase particle when unconstrained and the space (“hole”) put at its disposal by the matrix. Such misfit can arise due to specific volume differences induced by precipitation or by different thermal expansion or shrinkage upon heating
or cooling the specimen.
A possibly favourable effect of second-phase particles is a contribution to the enhancement of mechanical strength. Considering yielding of a material as related to glide of dislocations (Sect. 5.2.5), any mechanism obstructing dislocation glide improves the mechanical strength. In the discussion of the Frank–Read source for dislocation (-line) production (Sect. 5.2.6) it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of “antagonistic” nature and “block” propagation of the stress field of a migrating dislocation: the second-phase particle acts as “pinning point”. It was already indicated that in order that a dislocation can pass two pinning points (A and B in Fig. 5.13; see Sect. 5.2.6) a critical shear stress is needed
that depends on the distance between the obstacles (which can be second-phase particles):

\begin{equation} \label{eq:orowan} 
\tau_0 = Gb/d
\end{equation}

where d represents the distance between A and B and thus reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution. This mechanism for hardening is designated as the Orowan process (with $\tau_0$ as the Orowan
(shear) stress ; see also Sect. 11.14.4). As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles (see Fig. 5.27). Consequently, the effective average distance between the second-phase particles has decreased to d which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide (cf. (5.10)).
A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}. A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}. If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to

@@

	%\begin{figure}[ht]
	%	\centering
	%	\includegraphics[width=0.7\linewidth]{img/allline}
	%	\caption{Fracture process of specimen with void in $\alpha$ phase}
	%	\label{ }
	%\end{figure}
	%

@@

According to Schmid's law:
	$$\tau = \sigma*m$$
where m is the Schmid factor :
	$$ m = cos(\phi)cos(\lambda)$$
	%\subsection{The influence of void on strength of TiAl alloy}
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame2}
%		\caption{stress-$\sigma$=0}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame150}
%		\caption{stress-$\sigma$=0.15}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame160}
%		\caption{stress-$\sigma$=0.16}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame170}
%		\caption{stress-$\sigma$=0.17}
%		\label{ }
%	\end{figure}
%	
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame180}
%		\caption{stress-$\sigma$=0.18}
%		\label{ }
%	\end{figure}
%The location of void affects strength of material. Comparing with the model with integranular void, the model with %intergranular voids is weaker. atomic stress is calculated 
%	
%	
%	
%	
%	
%	% \begin{figure}[ht]
%	% 	\centering
%	% 	\includegraphics[width=0.7\linewidth]{img/ialine}
%	% 	\caption{stress-strain curve}
%	% 	\label{fig:ia_line}
%	% \end{figure}
%	% 
%	% \begin{figure}[ht]
%	% 	\centering
%	% 	\includegraphics[width=0.7\linewidth]{img/agline}
%	% 	\caption{stress-strain curve}
%	% 	\label{fig:ag_line}
%	% \end{figure}
%	
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/1stdiv}
%		\label{fig:surf}
%		\caption{stress-strain curve}
%	\end{figure}
%	
%	
%	\section{Conclusion}
%	%\bibliographystyle{elsarticle-num.bst}
%

\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

\subsection{Analysis method}
The centrosymmetry parameter is defined as follow:

	\begin{equation} \label{eq:csp} 
	P = \displaystyle\sum_{i=1}^{6}|\vec{R_i}+{\vec{R}}_{i+6}|^2
	\end{equation}

@@

\section{Results and Discussion}
%	/home/alex/Documents/violet/draft/img/perfect-line.pdf
The model without and type of void defect was regarded as benchmark of other simulation, deformation mechanisms was chose to . In order to examine deforamtion behaviour carefully, the whole tension process was sliced into four stages. Stage 1 is typical elasttic stage of the model, which is originate from strain $\epsilon = 0$ to $\epsilon = 0.09$. Stage 2 is yield stage of the model range from $\epsilon = 0.09$ to $\epsilon = $. stage 3.cracking stage and 4. Fracture stage. More specificially, a greater number of moments was snaped in stage 2 and stage 3.  
	\begin{figure}[ht]
		\centering
		\includegraphics[width=1\linewidth]{img/perfect-line2-2}
		\caption{perfect-line2-2}
		\label{fig:perfect-line2-2}
	\end{figure}

@@

\subsection{Evolution of spherical void in the simulation with intragranular spherical voids}
The volume defects considered pertain to three-dimensional objects contained within a matrix. Three-dimensional structures composed of zero-, one- or two-dimensional defects are not considered here.
Second-phase particles, precipitated within, as a consequence of a thermal treatment, or taken up, as a consequence of a material processing route, into a matrix of the first, dominant phase, disrupt, more or less (as possibly associated with
the occurrence of incoherent or coherent interfaces; see Sect. 5.3), the long-range translation symmetry of the matrix. They may induce considerable misfit-stress fields and thus can influence material properties pronouncedly. Such stress fields surrounding the second-phase particles can be due to misfit between the volume occupied by the second-phase particle when unconstrained and the space (“hole”) put at its disposal by the matrix. Such misfit can arise due to specific volume differences induced by precipitation or by different thermal expansion or shrinkage upon heating
or cooling the specimen.
A possibly favourable effect of second-phase particles is a contribution to the enhancement of mechanical strength. Considering yielding of a material as related to glide of dislocations (Sect. 5.2.5), any mechanism obstructing dislocation glide improves the mechanical strength. In the discussion of the Frank–Read source for dislocation (-line) production (Sect. 5.2.6) it was made clear that second-phase particles can serve as obstacles for dislocation migration: the stress fields surrounding the second-phase particles can be of “antagonistic” nature and “block” propagation of the stress field of a migrating dislocation: the second-phase particle acts as “pinning point”. It was already indicated that in order that a dislocation can pass two pinning points (A and B in Fig. 5.13; see Sect. 5.2.6) a critical shear stress is needed
that depends on the distance between the obstacles (which can be second-phase particles):
\begin{equation} \label{eq:orowan} 
\tau_0 = Gb/d
\end{equation}

where d represents the distance between A and B and thus reflects the dependence of the critical shear stress $\tau_0$ on the second-phase particle density and distribution. This mechanism for hardening is designated as the Orowan process (with $\tau_0$ as the Orowan
(shear) stress ; sgitee also Sect. 11.14.4). As a result of the Orowan process, upon passage of the pinning points by a series of gliding dislocations, a system of concentric loops is formed around the second-phase particles (see Fig. 5.27). Consequently, the effective average distance between the second-phase particles has decreased to d which implies a necessary increase of the value of critical shear stress required for continuation of dislocation glide (cf. (5.10)).
A step, of the width of a burgers vector, will be generated at both sidesof a crystal along teh direction of teh burgers vector after dislocation traversing teh entire crystal, as is shown in \ref{}. A small tep will be formed at spherical void surface toward teh void interiorafter dislocation absorptionat sphericalvoid surfaces, as is shown in \ref{}. If a great number of dislocation slip along their respective systemstowards teh spherical nanovoid in all directions, and are absorbed at spherical void surfaces, the spherical nanovoid will eventually shrink from teh dash circle to

@@

	%\begin{figure}[ht]
	%	\centeringT
	%	\includegraphics[width=0.7\linewidth]{img/allline}
	%	\caption{Fracture process of specimen with void in $\alpha$ phase}
	%	\label{ }
	%\end{figure}
	%

@@

According to Schmid's law:
	$$\tau = \sigma*m$$
where m is the Schmid factor :
	$$ m = cos(\phi)cos(\lambda)$$
	%\subsection{The influence of void on strength of TiAl alloy}
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame2}
%		\caption{stress-$\sigma$=0}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame150}
%		\caption{stress-$\sigma$=0.15}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame160}
%		\caption{stress-$\sigma$=0.16}
%		\label{ }
%	\end{figure}
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame170}
%		\caption{stress-$\sigma$=0.17}
%		\label{ }
%	\end{figure}
%	
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/frame180}
%		\caption{stress-$\sigma$=0.18}
%		\label{ }
%	\end{figure}
%The location of void affects strength of material. Comparing with the model with integranular void, the model with %intergranular voids is weaker. atomic stress is calculated 
%	
%	
%	
%	
%	
%	% \begin{figure}[ht]
%	% 	\centering
%	% 	\includegraphics[width=0.7\linewidth]{img/ialine}
%	% 	\caption{stress-strain curve}
%	% 	\label{fig:ia_line}
%	% \end{figure}
%	% 
%	% \begin{figure}[ht]
%	% 	\centering
%	% 	\includegraphics[width=0.7\linewidth]{img/agline}
%	% 	\caption{stress-strain curve}
%	% 	\label{fig:ag_line}
%	% \end{figure}
%	
%	
%	\begin{figure}[ht]
%		\centering
%		\includegraphics[width=0.7\linewidth]{img/1stdiv}
%		\label{fig:surf}
%		\caption{stress-strain curve}
%	\end{figure}
%	
%	
%	\section{Conclusion}
%	%\bibliographystyle{elsarticle-num.bst}
%	
\reftitle{References}
\bibliography{ref/VIOLET-ref.bib}
\end{document}
